Check Coverage

### 2019-10-22 analysis/merge_data.Rmd
Include number of traits in the data/metric table.

  fd_out <- as_tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .) %>%
    mutate(study_id = unlist(study), plot = unlist(plot_num)) %>%
    write_tsv(paste0(here::here("data"), "/fd_output/", "s", study, "_p", plot_num, "_fd.tsv"))

>>>>

  fd_out <- as_tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .) %>%
    mutate(study_id = unlist(study), plot = unlist(plot_num), trait_count = dim(trait_mat)[2]) %>%
    write_tsv(paste0(here::here("data"), "/fd_output/", "s", study, "_p", plot_num, "_fd.tsv"))
